---
title: "Should they sign a prenup?"
author: "Brian Holt"
date: "08/20/2015"
output: html_document
toc: true
---

The original case study was set up with the man asking for a prenuptial agreement.

Several years ago I began giving different versions of the 4th case study.  I wondered whether students would treat the case differently if it was the woman requesting the prenuptial.

So, I started tracking the results.  



# First, here is how your class responded:

```{r,echo=F,message=F}
library(lubridate)
library(tidyverse)
```
```{r,echo=F}
df<- readRDS("caseStudy4.RDS")
```


```{r,echo=F}
df %>% filter(quarter == 'C233') %>% 
  group_by(Version,prenp,gender) %>% 
  summarise(n=n()) %>% 
    ggplot(aes(x=Version,y=n,group=prenp,color=prenp,label=n)) +
  geom_point()+
  geom_line()+
  labs(title="Should a Prenup be signed, by version and gender",y='count') +
  scale_y_continuous(limits = c(0, 8))+
  geom_text(aes(y = n + .5))+
  facet_wrap(~gender)
```


# all data




#  Version and prenup

```{r,echo=FALSE}
df %>% 
  group_by(Version,prenp) %>% 
  summarise(n=n()) %>% 
    ggplot(aes(x=Version,y=n,label=n,group=prenp,color=prenp))+
  geom_line() +
  geom_point()+
  #facet_wrap(~Version)+
    geom_text(aes(y = n + 2))+
  labs(y="count")
```


#  Version and Sex

```{r,echo=FALSE}
df %>% 
  group_by(Version,Sex,prenp) %>% 
  summarise(n=n()) %>% 
    ggplot(aes(x=Version,y=n,label=n,group=prenp,color=prenp))+
  geom_point()+
  geom_line() +
  facet_wrap(~Sex)+
    geom_text(aes(y = n + 2))+
  labs(y="count")
```


# by date

```{r}
df %>% 
  group_by(Version,Sex,prenp,Date) %>% 
  summarise(n=n()) %>% 
  ggplot(aes(x=Date,y=n))+
  geom_point()

```

```{r}
df %>% 
  filter(prenp=='Yes') %>% 
  group_by(Version,Sex,Date) %>% 
  summarise(n=n()) %>% 
  ggplot(aes(x=Date,y=n,group=Version))+
  geom_col()

```
