---
title: "Should they sign a prenup?"
author: "Brian Holt"
date: "`r Sys.Date()`"
output: slidy_presentation
toc: true
---

The original case study was set up with the man asking for a prenuptial agreement.

Several years ago I began giving different versions of the 4th case study.  I wondered whether students would treat the case differently if it was the woman requesting the prenuptial.

So, I started tracking the results.  



# First, here is how your class responded:

```{r class resonses,echo=F,message=F}
knitr::opts_chunk$set(echo = FALSE,message = F,warning = F)
library(lubridate)
library(tidyverse)
```
```{r,echo=F}
df<- readRDS("caseStudy4.RDS")
```


```{r,echo=F}
df %>% 
  #filter(quarter == 'C233') %>% 
  group_by(Version,prenp,gender) %>% 
  summarise(n=n()) %>% 
    ggplot(aes(x=Version,y=n,group=prenp,color=prenp,label=n)) +
  geom_point()+
  geom_line()+
  labs(title="Should a Prenup be signed, by version and Sex",y='count') +
  scale_y_continuous(limits = c(0, 8))+
      geom_text(aes(y = n + .5,label=n),show.legend = F)+
  facet_wrap(~gender)
```


# all data




# Version and prenup

```{r,echo=FALSE}
df %>% 
  mutate(prenp=factor(prenp,levels = c("Yes","No","neither"))) %>% 
  group_by(Version,prenp) %>% 
  summarise(n=n()) %>% 
    ggplot(aes(x=Version,y=n,color=prenp,group=prenp))+
  geom_line() +
  scale_color_manual(values=c('cornflowerblue','darkred','darkgreen'))+
  geom_point()+
  #facet_wrap(~Version)+
    geom_text(aes(y = n + 4,label=n),show.legend = F)+
  labs(y="count",
       x= "Version; \nA=Man owns house\nB = Woman owns house")+
  ggtitle("Count of students answering yes/no \nto the question 'should they sign a prenup' ")
```


#  Version and Sex

```{r,echo=FALSE}
df %>% 
  group_by(Version,Sex,prenp) %>% 
  summarise(n=n()) %>% 
    ggplot(aes(x=Version,y=n,label=n,group=prenp,color=prenp))+
  geom_point()+
  geom_line() +
  facet_wrap(~Sex)+
        geom_text(aes(y = n + 4,label=n),show.legend = F)+
  labs(y="count",
       x= "Version; \nA=Man owns house\nB = Woman owns house")+
  ggtitle("Count of male and female students \nanswering yes/no to the question \n'should they sign a prenup' ")
  scale_color_manual(values=c('cornflowerblue','darkred','darkgreen'))
```


# by date

So, it's hard to show counts over time.  Creates messy graphs.  Maybe a cumulative line chart? 

Here is a line chart

```{r}
df %>% 
  group_by(Version,Sex,prenp,Date,quarter) %>%
  arrange(Date) %>% 
  summarise(n=n()) %>% 
  ggplot(aes(x=Date,y=n,color=prenp))+
  geom_line()+
  scale_color_manual(values=c('cornflowerblue','darkred','darkgreen'))+
  facet_wrap(~prenp)

```

# ratio of yes to other choices


We can, howeve, create a ratio which makes it a bit easier to see:




```{r, group by date/version}
 df %>%
    group_by(Date,Version,quarter,prenp) %>%
    summarise(n=n()) %>%
    pivot_wider(names_from =  prenp, values_from = n,values_fill = 0) %>% 
  mutate(prop_yes = Yes/(No+neither)) %>%

    ggplot(aes(x =Date, y=prop_yes,color=Version))+
    geom_point()#+#geom_line()+
  # scale_color_manual(values=c('cornflowerblue','darkred','darkgreen'))

```
